### 2024-08-27 paper.tex
future work

\section{Finding the irreducible components of a springer fiber at a slodowy slice}
Apply things from the previous two sections, and conclude.

@@

>>>>

\section{The components of \(\mathcal{P}_{J(\lambda)}\)}
Apply things from the previous two sections, and conclude.

@@

\section{Future work}
The paper (TODO: cite) describes a correspondence between Steinberg variety and pairs of young tableaux.  
We observe that \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) looks something liek the stienber variety.
Maybe there is a similar correspondence, between elements of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) and pairs of yound tableaux: one of shape of \(X\), one of shape of \(A_{X, a, b}\).
\par Separately, this paper could use a nice introductory section where we motivate the study of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
